Atomify - a live LAMMPS visualizer

### 2017-06-16 ms.tex
Added text on future work and data-pipeline figures

The main features of Atomify are script editing,
live visualization, and live plotting of computed quantities.
These will be described in detail in the following paragraphs.
In addition, Atomify comes packaged with multiple examples,
many of which have been made by members of the LAMMPS community.
These examples are easily explored within Atomify.

% TODO list other, smaller features that are not in the following subsections or create more subsections for bigger features

\subsection{Script editor}

@@

\subsection{Visualization}

@@

\subsection{Dashboard}

@@

Parameters for rendering, such as the light strength and color,
can be modified in the Rendering tab of the dashboard.
See the above section about the script editor for information about how to
modify the color of the particles.

@@

\subsection{Live plotting}
TODO: Histogram over per atom quantities \\
TODO: Time evolution of quantity \\
TODO: 2d ave/chunk binning \\

In LAMMPS, computes are physical quantities calculated based on the running
simulation, such as energy, temperature and stress.
% TODO better word for measures?
These are typically macroscopic measures derived from the microscopic
interactions between the atoms.

@@

\subsection{Future work}
Atomify is far from finished.\\
A web version of Atomify is in development using WebGL and Emscripten. \\
Geometry shaders \\
Improved script editor with auto completion \\
Moltemplate interface \\

@@

>>>>

The main features of Atomify are script editing,
live visualization, and live plotting of computed quantities.
In addition, Atomify comes packaged with multiple examples,
many of which have been made by members of the LAMMPS community.
These examples are easily explored within Atomify.

@@

@@

@@

Parameters for rendering, such as the light strength,
attenuation, and color can be modified in the Rendering tab of the dashboard.
See the above section about the script editor for information about how to
modify the color of the particles.

@@

TODO: Time evolution of quantity \\
TODO: 2d ave/chunk binning \\

In LAMMPS, computes are physical quantities calculated based on the running
simulation, such as energy, temperature and stress.
% TODO better word for measures?
These are typically macroscopic measures derived from the microscopic
interactions between the atoms.
These can be plotted as a function of time and visualized while the 
simulation is running.
Quantities that are measured per atom can be plotted in a histogram.

@@

\subsection{Future work}

Atomify continues in heavy development and we have several features planned for
future versions.
A web version of Atomify using WebGL and WebAssembly will make it easy to test
scripts in the browser.
This is useful in educational settings where teachers wish to introduce students
to LAMMPS without installing additional software.
It will also serve as a nice demonstration of the full desktop application of
Atomify.

Performance improvements are planned by for instance using geometry shaders to
generate periodic copies.
Currently this is partially done on the CPU,
which  reduces performance drastically.
We also aim to include more backends, both using the CPU and GPU,
in addition to running simulations on computing clusters while visualizing them
on the users own computer.

The script editor will get features such as autocompletion of LAMMPS commands
and easy access to the online documentation by hovering or selecting specific
commands.

We are also working on including Moltemplate and other programs that generate
systems to make it easier for users to get started with more complex
simulations.

@@

Atomify is availabe on Linux, MacOS and Windows and can be downloaded from
\href{https://ovilab.net/atomify}{http://ovilab.net/atomify}.
A lightweight version of the desktop application is also available for mobile
devices running Android or iOS.
